Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2017-07-09 documentation/userguide.tex
Update Microphysics URL

This software requires a few other software packages to be installed before it can be used.
The science software includes \href{https://github.com/AMReX-Codes/amrex}{AMReX} and 
\href{https://github.com/AMReX-Astro/Castro}{CASTRO}. \castro\ will also need
the \href{https://github.com/BoxLib-Codes/Microphysics}{Microphysics} repository, 
which stores the equation of state and nuclear network we will use. Instructions for
building and installing \castro\ can be found in its documentation.
This package relies on several utilities that are
commonly distributed on Linux systems: \texttt{bash}, \texttt{GNU bc}, \texttt{GNU make}, 
\texttt{batch}, \texttt{GNU sed}, and \texttt{GNU awk}. Analysis is mainly performed in 
\href{https://www.python.org/}{python}, with the \href{http://matplotlib.org/}{matplotlib} 
library and the \href{http://yt-project.org/}{yt} code being used for visualization. 
If python and yt are not installed on your system, you will still be able to compile and 
run this code, but we use yt for all analysis of \amrex\ output data other than 
the ASCII files that are generated at runtime. We have some routines for this purpose 
available in Fortran and Python; some of the Fortran tools are provided in \amrex\ 
itself, in the \texttt{Tools/Postprocessing} subdirectory, and it is straightforward enough 
to modify them for basic analysis. We may be able to provide others upon request.

>>>>

This software requires a few other software packages to be installed before it can be used.
The science software includes \href{https://github.com/AMReX-Codes/amrex}{AMReX} and 
\href{https://github.com/AMReX-Astro/Castro}{CASTRO}. \castro\ will also need
the \href{https://github.com/starkiller-astro/Microphysics}{Microphysics} repository, 
which stores the equation of state and nuclear network we will use. Instructions for
building and installing \castro\ can be found in its documentation.
This package relies on several utilities that are
commonly distributed on Linux systems: \texttt{bash}, \texttt{GNU bc}, \texttt{GNU make}, 
\texttt{batch}, \texttt{GNU sed}, and \texttt{GNU awk}. Analysis is mainly performed in 
\href{https://www.python.org/}{python}, with the \href{http://matplotlib.org/}{matplotlib} 
library and the \href{http://yt-project.org/}{yt} code being used for visualization. 
If python and yt are not installed on your system, you will still be able to compile and 
run this code, but we use yt for all analysis of \amrex\ output data other than 
the ASCII files that are generated at runtime. We have some routines for this purpose 
available in Fortran and Python; some of the Fortran tools are provided in \amrex\ 
itself, in the \texttt{Tools/Postprocessing} subdirectory, and it is straightforward enough 
to modify them for basic analysis. We may be able to provide others upon request.
